replication_report

### 2015-03-28 replication_report.Rmd
Add work to Rmd file

#load data:
dat <- read.csv("GORN_study3.csv", header = TRUE)
head(dat)
View(dat)

@@

@@

```{r, echo=FALSE}
##Scatterplots
graph.simple = ggplot(dat, aes(x = wmc.center, y = stroop.rt)) 
graph.simple + geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("Simple Effect of Working Memory on Stroop Performance (RT)") +
  ylab("Stroop RT") +
  xlab("Working Memory Deviation Score from Mean")

graph.moderator = ggplot(dat, aes(x = X.center, y = Y, colour = M)) 
graph.moderator + geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("Working Memory on Stroop Performance (RT)") +
  ylab("Stroop RT") +
  xlab("Working Memory Deviation Score from Mean")
```

>>>>

#load data:
dat <- read.csv("GORN_study3.csv", header = TRUE)
dat <-tbl_df(dat)
View(dat)
dat %>%
  filter(na.rm=TRUE) %>%
  group_by(Groep) %>%
  summarise(total.n = n())

by_group<-group_by(dat, Groep)
mutate(distinct_groups= count(n_distinct(Groep))
summarise(distinct_groups)
count(dat, distinct_groups(N()))

#GOT IT TO WORK:
ddply(dat,.(Groep),
      summarise,
      count = length(form_nr1)
      )

@@

#Work on tables:
# CODE FOR TABLE HERE:
install.packages("tables")
library(tables)
install.packages("mosaic")
library(mosaic)
install.packages("stargazer")
library(stargazer)
install.packages("xtable")
library(xtable)

# using tables function, doesnt work as planned
csvtable<-tbl_df("Experiment3_ReplicationTable_csv.csv")
view(csvtable)

tabular(dat_egood$music + 1) ~ (n+1) + Format(digits=2)* 
          (dat_egood$chose_advertised_pen)* (n+ proportions), data=dat_egood)))

#not what expected
mosaicplot(freqtable)

# better
attach(dat_egood)
freqtable<-table(dat_egood$music,dat_egood$chose_advertised_pen)
freqtable
margin.table(freqtable, 1)
margin.table(freqtable, 2)
prop.table(freqtable)
proportions <-prop.table(freqtable, 1)
proportions
prop.table(freqtable, 2)

# trying stargazer... no good
stargazer(dat_egood[c("")], type= "text", title= "Frequencies...", digits=2, out="freqtable.txt")

#
tbl2<-tbl_df(tbl2)
print(xtable(tbl2), type="html")

@@

```{r, echo=FALSE}
##Scatterplots
graph.simple = ggplot(dat, aes(x = wmc.center, y = stroop.rt)) 
graph.simple + geom_smooth(method = "") +
  geom_point() +
  ggtitle("") +
  ylab("") +
  xlab("")

graph.moderator = ggplot(dat, aes(x = X.center, y = Y, colour = M)) 
graph.moderator + geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("") +
  ylab("") +
  xlab("")
```
